\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-13 manuscript.tex
* Invariance explained

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Helvetica}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Development of a novel instrument to capture light exposure-related behaviours},
  pdfauthor={Mushfiqul Anwar Siraji1, *, Rafael Robert Lazar2, 3, *, Juliëtte van Duijnhoven4, Luc Schlangen5, Shamsul Haque1, Vineetha Kalavally6, Céline Vetter7, 8, Gena Glickman9, Karin Smolders10, \& Manuel Spitschan11, 2, 3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Age among all participants ranged from 11 years to 84 years {[}EFA: \emph{min} = 11, \emph{max} = 84; CFA: \emph{min} = 12, \emph{max} = 74{]}, with an overall mean of \textasciitilde{} 33 years of age {[}Overall: \emph{M} = 32.95, \emph{SD} = 14.57; EFA: \emph{M} = 32.99, \emph{SD} = 15.11; CFA: \emph{M} = 32.89, \emph{SD} = 13.66{]}. In total 325 (47\%) of the participants indicated female sex {[}EFA: 189 (44\%); CFA: 136 (52\%){]}, 351 (51\%) indicated male {[}EFA: 230 (54\%); CFA: 121 (46\%){]} and 14 (2.0\%) indicated other sex {[}EFA: 9 (2.1\%), CFA: 5 (1.9\%){]}. Overall, 49 (7.2\%) {[}EFA: 33 (7.8\%); CFA: 16 (6.2\%){]} participants indicated a gender-variant identity. In a ``Yes/No'' question regarding native language, 320 (46\%) of respondents {[}EFA: 191 (45\%); CFA: 129 (49\%){]} indicated to be native English speakers. For their ``Occupational Status,'' more than half of the overall sample reported that they currently work {[}Overall: 396 (57\%); EFA: 235 (55\%); CFA: 161 (61\%){]}, whereas 174 (25\%) {[}EFA: 122 (29\%); CFA: 52 (20\%){]} reported that they go to school and 120 (17\%) {[}EFA: 71 (17\%); CFA: 49 (19\%){]} responded that they do ``Neither.'' With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 303 (44\%) {[}EFA: 194 (45\%); CFA: 109 (42\%){]} of the participants indicated that they were in a home office/ home schooling setting., while 109 (16\%) overall {[}EFA: 68 (16\%) ; CFA: 41 (16\%){]} reported face-to-face work/schooling. Lastly, 147 (21\%) overall {[}EFA: 94 (22\%) ; CFA: 53 (20\%){]} reported a combination of home- and face-to-face work/schooling, whereas 131 (19\%) overall {[}EFA: 72 (17\%); CFA: 59 (23\%){]} filled in the ``Neither (no work or school, or indication)'' response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable ``Age'' and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's ``add\_p'' function (Sjoberg et al., 2021a) . The p-values were corrected for multiple testing applying false discovery rate (FDR) via the ``add\_q'' function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values \emph{q} ≥ 0.2 , indicating equivalence).

@@

We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways). As our purpose was to capture light exposure related behavior, ``Does not apply/I don't know'' and ``Never'' were providing similar information. As such we decided to collapse ``Does not apply/I don't know'' and ``Never'' options into one making it a 5 point Likert type response scale. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C. Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (PA) as a factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well. We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018) We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.

@@

In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86). All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71). Items under this factor commonly investigate an individual's hours spent outdoor. The third factor contained five items and explained 8.83\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to sleep. The internal consistency reliability coefficient was, \(\alpha\) = .68. The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62. These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time. Lastly, the fifth factor contained six items and explained 6.14\% of the total variance. This factor tried to measure an individual's behavior lead by the awareness of light's influence on health. However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53). It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(C. Desjardins \& Bulut, 2018). Several indices are suggested to measure model fit. These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015). Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit. Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the chi-square test. However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015). Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y. Yu, 2002). Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = .12). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999). Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct (Sijtsma, 2009) we report Mcdonald's omega(total) as the internal consistency reliability coefficient. Mcdonald's omega(total) is reported to be a satisfactory lower bound reliability coefficient that works for both unidimensional and multidimensional construct (Zinbarg, Revelle, Yovel, \& Li, 2005). Mcdonald's omega(total) for the five factors were .90, .80, .61, .72, .45 respectively. Mcdonald's omega(total) coefficient for the total scale was .73.

@@

@@

\scriptsize{

\begin{longtable}{cccccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:InvarianceTab}Invariance Analysis}\\
\toprule
 & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{SRMR} & \multicolumn{1}{c}{Chi-Sqr comparison} & \multicolumn{1}{c}{df*} & \multicolumn{1}{c}{p}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:InvarianceTab} continued}}\\
\toprule
 & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{SRMR} & \multicolumn{1}{c}{Chi-Sqr comparison} & \multicolumn{1}{c}{df*} & \multicolumn{1}{c}{p}\\
\midrule
\endhead
Configural & 632.20 & 442.00 & 0.95 & 0.94 & 0.06 & 0.05 & 0.07 & 0.13 & - & - & -\\
Metric & 644.58 & 458.00 & 0.95 & 0.95 & 0.06 & 0.05 & 0.07 & 0.13 & 18.019a & 16 & 0.323\\
Scalar & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0.13 & 67.961b & 64 & 0.344\\
Residual & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0.13 & 0c & 0 & NA\\
Structural & 691.49 & 542.00 & 0.96 & 0.96 & 0.05 & 0.04 & 0.06 & 0.13 & 12.617d & 20 & 0.893\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

@@

@@

@@

@@

@@

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Development of a novel instrument to capture light exposure-related behaviours},
  pdfauthor={Mushfiqul Anwar Siraji1, *, Rafael Robert Lazar2, 3, *, Juliëtte van Duijnhoven4, Luc Schlangen5, Shamsul Haque1, Vineetha Kalavally6, Céline Vetter7, 8, Gena Glickman9, Karin Smolders10, \& Manuel Spitschan11, 2, 3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Age among all participants ranged from 11 years to 84 years {[}EFA: \emph{min} = 11, \emph{max} = 84; CFA: \emph{min} = 12, \emph{max} = 74{]}, with an overall mean of \textasciitilde{} 33 years of age {[}Overall: \emph{M} = 32.95, \emph{SD} = 14.57; EFA: \emph{M} = 32.99, \emph{SD} = 15.11; CFA: \emph{M} = 32.89, \emph{SD} = 13.66{]}. In total 325 (47\%) of the participants indicated female sex {[}EFA: 189 (44\%); CFA: 136 (52\%){]}, 351 (51\%) indicated male {[}EFA: 230 (54\%); CFA: 121 (46\%){]} and 14 (2.0\%) indicated other sex {[}EFA: 9 (2.1\%), CFA: 5 (1.9\%){]}. Overall, 49 (7.2\%) {[}EFA: 33 (7.8\%); CFA: 16 (6.2\%){]} participants indicated a gender-variant identity. In a ``Yes/No'' question regarding native language, 320 (46\%) of respondents {[}EFA: 191 (45\%); CFA: 129 (49\%){]} indicated to be native English speakers. For their ``Occupational Status,'' more than half of the overall sample reported that they currently work {[}Overall: 396 (57\%); EFA: 235 (55\%); CFA: 161 (61\%){]}, whereas 174 (25\%) {[}EFA: 122 (29\%); CFA: 52 (20\%){]} reported that they go to school and 120 (17\%) {[}EFA: 71 (17\%); CFA: 49 (19\%){]} responded that they do ``Neither.'' With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 303 (44\%) {[}EFA: 194 (45\%); CFA: 109 (42\%){]} of the participants indicated that they were in a home office/ home schooling setting., while 109 (16\%) overall {[}EFA: 68 (16\%) ; CFA: 41 (16\%){]} reported face-to-face work/schooling. Lastly, 147 (21\%) overall {[}EFA: 94 (22\%) ; CFA: 53 (20\%){]} reported a combination of home- and face-to-face work/schooling, whereas 131 (19\%) overall {[}EFA: 72 (17\%); CFA: 59 (23\%){]} filled in the ``Neither (no work or school, or indication)'' response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable ``Age'' and Pearson's \(\chi^2\) test for all other categorical variables via the gtsummary R package's ``add\_p'' function (Sjoberg et al., 2021a) . The p-values were corrected for multiple testing applying false discovery rate (FDR) via the ``add\_q'' function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values \emph{q} ≥ 0.2 , indicating equivalence).

@@

We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always). As our purpose was to capture light exposure related behavior, ``Does not apply/I don't know'' and ``Never'' were providing similar information. As such we decided to collapse ``Does not apply/I don't know'' and ``Never'' options into one making it a 5 point Likert type response scale. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C. Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (PA) as a factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well. We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018) We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.

@@

Internal consistency reliability coefficient Cronbach's alpha assumes that all the factor- loading of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample. Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature (Gadermann, Guhn, \& Zumbo, 2012; Zumbo, Gadermann, \& Zeisser, 2007). Subsequently to get better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous. Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability. In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .94. All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 9.93\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .76. Items under this factor commonly investigate an individual's hours spent outdoor. The third factor contained five items and explained 8.83\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to sleep. The internal consistency reliability coefficient was, ordinal \(\alpha\) = .75. The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, ordinal \(\alpha\) = .72. These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time. Lastly, the fifth factor contained six items and explained 6.14\% of the total variance. This factor tried to measure an individual's behavior lead by the awareness of light's influence on health. The internal consistency reliability was, ordinal \(\alpha\) = .62 . It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(C. Desjardins \& Bulut, 2018). Several indices are suggested to measure model fit. These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015). Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit. Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the \(\chi^2\) test. However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015). Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y. Yu, 2002). Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = .12). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).

Internal consistency ordinal \(\alpha\) for the five factors of LEBA were .96, .83, .70, .69, .52 respectively. We also estimated the internal consistency reliability of the total scale using Mcdonald's omega(total) coefficient which is a better reliability estimate for multidimensional constructs(Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009). McDonald's omega(total) coefficient for the total scale was .73.

@@

\hypertarget{measurement-invariance}{%
\section{Measurement Invariance}\label{measurement-invariance}}

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016). We used structural equation modeling framework to assess measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}. Our measurement invariance testing involved establishing configural, metric , scalar , and residual invariance (Widaman \& Reise, 1997). MI models are nested type models of which configural model is the first and least restrictive model. Configural model assumes that the number of factors and item number under each factors will be equal across two groups. Metric invariance model along with the assumption of configural model assumes that factor-loadings of the items across the two groups will be equal indicating each item contributes to the measured construct equivalently for the both groups. Along with these assumptions scalar invariance assumes that item intercepts to be equivalent across groups. Scalar invariance model indicates the equivalence of response scale across the groups, i.e.~persons with the same level of the underlying construct will score the same across the groups. Residual invariance model holds all the mentioned assumptions as true and also adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above) , RMSEA (close to .06 or below). following the guidelines of Hu and Bentle (1999). We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y. Yu, 2002). Table \ref{tab:InvarianceTab} summarized the fit indices. The comparison among different measurement invariance model was made by using \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI. If the \(\Delta \chi^2\) is not statistically significant (p\textless0.05) (Dimitrov, 2010) the particular invariance model was accepted. We started our analysis by comparing the model fit of the lest restrictive model:configural model to metric MI model and continued successive comparisons. Table \ref{tab:InvarianceTab} indicates that our fiited model attains residual invariance: the highest level of invariance in terms of CFI, TLI, RMSEA and non-significant \(\Delta \chi^2\) test.

@@

\footnotesize{

\begin{longtable}{ccccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:InvarianceTab}Invariance Analysis}\\
\toprule
 & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{Chi-Square Difference} & \multicolumn{1}{c}{df difference*} & \multicolumn{1}{c}{p}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:InvarianceTab} continued}}\\
\toprule
 & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{Chi-Square Difference} & \multicolumn{1}{c}{df difference*} & \multicolumn{1}{c}{p}\\
\midrule
\endhead
Configural & 632.20 & 442.00 & 0.95 & 0.94 & 0.06 & 0.05 & 0.07 & - & - & -\\
Metric & 644.58 & 458.00 & 0.95 & 0.95 & 0.06 & 0.05 & 0.07 & 18.019a & 16 & 0.323\\
Scalar & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 67.961b & 64 & 0.344\\
Residual & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0c & 0 & NA\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-dimitrov2010testing}{}}%
Dimitrov, D. M. (2010). Testing for factorial invariance in the context of construct validation. \emph{Measurement and Evaluation in Counseling and Development}, \emph{43}(2), 121--149.

@@

\leavevmode\vadjust pre{\hypertarget{ref-dunn2014alpha}{}}%
Dunn, T. J., Baguley, T., \& Brunsden, V. (2014). From alpha to omega: A practical solution to the pervasive problem of internal consistency estimation. \emph{British Journal of Psychology}, \emph{105}(3), 399--412.

@@

\leavevmode\vadjust pre{\hypertarget{ref-gadermann2012estimating}{}}%
Gadermann, A. M., Guhn, M., \& Zumbo, B. D. (2012). Estimating ordinal reliability for likert-type and ordinal item response data: A conceptual, empirical, and practical guide. \emph{Practical Assessment, Research, and Evaluation}, \emph{17}(1), 3.

\leavevmode\vadjust pre{\hypertarget{ref-graham2006congeneric}{}}%
Graham, J. M. (2006). Congeneric and (essentially) tau-equivalent estimates of score reliability: What they are and how to use them. \emph{Educational and Psychological Measurement}, \emph{66}(6), 930--944.

@@

\leavevmode\vadjust pre{\hypertarget{ref-novick1967coefficient}{}}%
Novick, M. R., \& Lewis, C. (1967). Coefficient alpha and the reliability of composite measurements. \emph{Psychometrika}, \emph{32}(1), 1--13.

@@

\leavevmode\vadjust pre{\hypertarget{ref-putnick2016measurement}{}}%
Putnick, D. L., \& Bornstein, M. H. (2016). Measurement invariance conventions and reporting: The state of the art and future directions for psychological research. \emph{Developmental Review}, \emph{41}, 71--90.

@@

\leavevmode\vadjust pre{\hypertarget{ref-widaman1997exploring}{}}%
Widaman, K. F., \& Reise, S. P. (1997). Exploring the measurement invariance of psychological instruments: Applications in the substance use domain.
